---
title: "Lab 5"
author: "Daija Odom"
date: "10/25/2021"
output: 
  html_document: 
    theme: cosmo
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too.

```{r}
# Create a mock sample

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29, 90, 72, 112)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# df refers to degrees of freedom which is your (sample?) mean minus 1

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```

If we took multiple samples from this population and calculate a confidence interval for each, we would expect 95% of the confidence intervals to contain the population mean.

Mean otter length is 36.9 inches $\pm$ 9.3 (mean$\pm$ sd, n= 8) with a 95% confidence interval of [29.1, 44.7] inches.

To call elements from a list use `objectname$valuename`
ex. otter_ci$p.value

#### Now, using in-line referencing
By using r with surrounding tick marks you are inserting a mini code chunk. You can hover over the mini code chunk and press command + enter to see the values.

Mean otter length `r round(otter_ci$estimate, 1)` inches.
