---
title: "Lab 5"
author: "Daija Odom"
date: "10/25/2021"
output: 
  html_document: 
    theme: cosmo
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too.

```{r}
# Create a mock sample

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29, 90, 72, 112)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# df refers to degrees of freedom which is your (sample?) mean minus 1

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```

If we took multiple samples from this population and calculate a confidence interval for each, we would expect 95% of the confidence intervals to contain the population mean.

Mean otter length is 36.9 inches $\pm$ 9.3 (mean$\pm$ sd, n= 8) with a 95% confidence interval of [29.1, 44.7] inches.

To call elements from a list use `objectname$valuename`
ex. otter_ci$p.value

#### Now, using in-line referencing
By using r with surrounding tick marks you are inserting a mini code chunk. You can hover over the mini code chunk and press command + enter to see the values.
Use round(, 1) to round the decimal place to how many places you want after the decimal

Mean otter length `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1)` , `r round(otter_ci$conf.int[2], 1)`] inches.


## Part 2: Two-sample t-tests

### Example 1

Make two mock samples and ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?

```{r}
# Make my mock samples
oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25)

pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

# Two-sample t-test
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same
# i.e: Trees are drawn from populations with the same mean height

# The p-value means if these samples were drawn from samples with the same mean height, there is a 28.7 percent chance of taking a random sample and finding that  are at least different as the ones we found by random chance.
# You do not have enough evidence to reject the null hypothesis
```

The mean heights of oak and pine trees were (x +- Y) and (x +- Y), respectively, and the difference was not significant (t(`r trees_t$parameter`) = `r round(trees_t$statistic, 1)`, p = `r trees_t$p.value`).

"t(df) = t-statistic,  p = p-value"


*Avoid* ever saying: p = 0

When things get really small (usually p < 0.001)

*Not great:* p = 0.0000000013
*Better:* p < 0.001

## Part 3: Another t-test with cars data

Using the `mpg` dataset

### Take a look at the data

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))

# Check for remaining levels
# Unique() tells you if your filter() worked 
unique(compact_suv$class)
```

Create a histogram of city gas mileage (cty) faceted by class starting from compact_suv.

```{r}
#bins = # changes the number of bins on graph, default is 30

ggplot(data = compact_suv, aes(x = cty)) +
  geom_histogram(bins = 10) +
  facet_wrap(~ class)

#geom_qq is a quantile-quantile plot
ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~ class)

```
Find some summary statistics for each group.

```{r}

car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city = round(mean(cty), 2),
    sd_city = sd(cty),
    sample_size = n()
  )
# Always check your summary statistics to see if they at least make sense
car_stats
```

The t.test() function REALLY wants vectors of things. USe the `pull()` function to pull out a vector from a data frame.

```{r}

compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

# Your turn: do the same thing to get a vector of city gas mileages for SUVs
suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)

```

Use a t-test to find null hypothesis
H0: Mean city gas mileages for SUVs and compact cars are the same

```{r}
t.test(compact_sample, suv_sample)
```

There is a significant difference in mean city gas mileage for SUVs and compact cars (t(df) = t-statistic, p < 0.001)
